Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-03 Rapport/Article/Article.tex
Seance 06/03/2019

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{verbatim}

@@

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/test}
    \caption{Diagram of a simplified communication system.}\label{fig:cs}
\end{figure}

@@

\subsection{Notation}
Special notations used throughout the paper as shown in figures tac tac

@@

\begin{align}
	\text{ReLU: } \sigma_1 (x)& = max\{0, x\} \label{eq:relu}\\ 
	\text{Sigmoid: } \sigma_2 (x)& = \frac{1}{1+e^{- \lambda x}} \label{eq:sig}
\end{align}
where $x \in \mathbb{R}$.

@@

\subsection{Autoencoders}
TO PARAPHRASE: The parallel computing
capabilities of NNs allow us to solve or, at least, approximate
the MLD problem in polynomial time [7]. Moreover, the
weights of the NN are precomputed during training and the
decoding step itself is then relatively simple.

NNs which can learn an appropriate
mapping between noisy input patterns and codewords. No
assumption has to be made about the statistics of the channel
noise because the NN is able to learn the mapping or to
extract the channel statistics during the learning process

decoding problems have far more possibilities than conventional pattern recognition problems

In 2006, a new training technique, called layer-by-layer
unsupervised pre-training followed by gradient descent finetuning [14], led to the renaissance of NNs because it made
training of NNs with more layers feasible.

new hardware such as graphical processing units (GPUs) are available
to speed up learning as well as inference. In this renaissance
of NNs, new NND ideas emerge

The curse of dimensionality

@@

\subsection{Array Decoder}
Architecture, Training parameters, cite choice of p train \cite{b13}, number of epochs, Talk about noise layer and its removal in prediction,

\subsection{One-hot Decoder}
Architecture, Training parameters, Explain what is a One hot decoding, talk about the matrix transformation from one hot to messages, p train equals 0, number of epochs

@@

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}

\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{verbatim}

@@

@@

\subsection{Notation}
Throughout the work, vectors will be written in bold font weight and may  have a subscript which indicates their layer in a NN and may have a superscript which indicates their size length. In order to homogenize notation, for the encoding phase of the communication system, $\textbf{u}^k$ represents an input \textit{source message} and $\textbf{x}^n$ its correspondent codeword. For the decoding portion, $\textbf{y}^n$ represents the output of the noisy channel and $\hat{\textbf{u}}^k$ the estimated source message. These definitions are illustrated in Fig. \ref{fig:cs}.

In addition, every indispensable concept is introduced either in italics or is defined by a commonly used abbreviation present in others scientific works.

@@

\begin{align}
	\text{ReLU: } \sigma_1 (x)& = max\{0, x\} \label{eq:relu}\\ 
	\text{Sigmoid: } \sigma_2 (x)& = \frac{1}{1+e^{- \lambda x}} \label{eq:sig}
\end{align}
where $x \in \mathbb{R}$ and $\lambda>0$.

@@

\subsection{Autoencoders}

Autoencoders based on DNN can learn an appropriate correspondence between input source messages and estimated source message output through different noisy channels. The statistics of the channel's noise is shown in \cite{2018} to be irrelevant, since the NN extract it during training phase. Their applicability is tantamount compelling because the weights computed during training can be separated in two groups, one correspondent to the nodes before the channel and one posterior to the channel. As a consequence, we are able to design an non linear encoder and its correspondent non linear decoder with substantial ease. This new representation has ultimately far more possibilities than conventional encoding patterns.

Whilst autoencoders are more complex dimensional wise when compared to NN decoders, the readily access to graphical processing units (GPUs) contributed to the feasibility of this technique, tackling the \textit{curse of dimensionality} challenge in ML. This type of hardware made possible the approach of the layer-by-layer unsupervised pre-training followed by stochastic gradient descent applied in this work. \cite{GPU}

@@

\subsection{Decoder}
Hamming coding

The linear encoding matrix $\textbf{G}_{8\times16}$ is shown below.

\begin{flalign*}
    &\textbf{G}=&
\end{flalign*}

\[
\left [
  \begin{array}{cccccccccccccccc}

   1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
	1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 & 0 & 0 & 0 \\
	1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
	1 & 0 & 1 & 0 & 1 & 0 & 1 & 0 & 1 & 0 & 1 & 0 & 1 & 0 & 1 & 0 \\
	1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
  \end{array}
\right ]
\]

Introduce encoding equations

\subsubsection{Array Decoder}
Architecture, Training parameters, cite choice of p train \cite{b13}, number of epochs, Talk about noise layer and its removal in prediction, 
\subsubsection{One-hot Decoder}
Architecture, Training parameters, Explain what is a One hot decoding, talk about the matrix transformation from one hot to messages, p train equals 0, number of epochs

@@

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/MAP_MLNN1H_p_0}
    \caption{Test caption to test image.}\label{fig:1HD}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/MAP_MAP_Mep_65536}
    \caption{Test caption to test image.}\label{fig:ae1}
\end{figure}

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{images/MAP_AutoencoderArray_Mep_65536}
    \caption{Test caption to test image.}\label{fig:ae1}
\end{figure}

@@

\bibitem{GPU} G. E. Hinton, S. Osindero, and Y.-W. Teh, “A fast learning algorithm for deep belief nets,” Neural Computation, vol. 18, no. 7, pp. 1527–1554, July 2006.
